\begin{acknowledgements}

First and foremost I would like to acknowledge my advisor, Katie Byl, for her support and mentorship throughout my PhD. She welcomed me into her lab, offered me the guidance to get started, and the freedom to explore the many different research topics that I was interested in. I would also like to extend my thanks to the rest of my committee, Joao Hespanha, Linda Petzold, and Yon Visell, for their feedback and support.

I would also like to thank the other members of the UCSB robotics lab that I had the privilege of working beside. Guillaume Bellegarda, Nihar Talele, Asutay Ozmen, Thomas Ibbetson, Roman Aguillera, Sean Anderson, and Chris Cheney. Guillaume and Nihar in particular were the senior members of the lab when I first joined, and they were role models and offered invaluable guidance. Additionally, I would like to acknowledge the visiting students that I had to privilege to work with and mentor, Marco Molnar, Nina Grabka, and Min Dai. 

I also need to thank all of my friends that supported me throughout this time. Both my old friends: Fraser Hood, Haris Godil, Colin Briber, Holden Smith, and Stephanie Dang; and the many new friends I have met during my time in this PhD program: Nathan Tucker, Rahul Chandan, Chris Salls, Chani Jindal, Bryce Ferguson.

%\todo {Decide who else makes the cut ... or if I should make an even shorter list Liz? My Entire DnD group? Keith? Michael Choquer Sharad Shankar , Brian Canty } 

My Mother, Father, and brother Kyle all deserve extensive thanks for their unending support and care. Lastly I thank my partner, Jennifer Chan, for her love, support, and encouragement during final stage of my PhD.


\end{acknowledgements} 